Learning to Synthesize Rules for Network Intrusion Detectors

### 2020-01-06 paper/paper.tex
pass on workflow (input and output)
pass

\tname{} is a technique that uses (1) benign and malicious network
traffic and (2) existing signature-based \nids\ rules to synthesize
new rules. The goal of \tname\ is to create plausible rules that
\emph{only} captures the positive traffic, \ie{}, the malicious
messages.

\Mar{----------------------------------- estou aqui}

\begin{figure*}[t]
\centering
\includegraphics[trim=0 300 350 0,clip,width=0.95\textwidth]{figs/nids-workflow}
\caption{\tname\ workflow.}
\label{fig:overview}
\end{figure*}

\vspace{1ex}
\noindent\textbf{Overview.}~ The input of the technique is the
positive traffic whereas the output is a list of minimized rules
capturing only the positive, malicious,
traffic. Figure~\ref{fig:overview} shows the workflow of \tname{} as a
pipeline of two components, which appear numbered in the figure.
\tname{} synthesizes rules in two steps. First, it produces a
potentially overspecified rule that captures the malicious traffic
provided on input. In this step, \tname\ finds options by
\emph{reverse engineering} the positive traffic. It extracts tokens
from the malicious message and uses them to define the initial
rule. We say that this rule overfits the problem as it satisfies the
success criterion of only capturing the positive traffic, however it
is unlikely that it will be able to generalize to other attacks,
\ie{}, attacks of the same kind, but with different data. The reason
is that many options added to the rule are unimportant for
discriminating the attack. In the second step, \tname{} uses negative
examples to \emph{minimize} the rule, discarding unnecessary
options. Note that any subset of the original set of options captures
the positive traffic. The minimization step uses a population-based
gradient descent-like search to generate minimal solutions.

@@

%\begin{wrapfigure}[15]{r}{0.56\textwidth}
\begin{figure}[t!]
  \centering
  \vspace{-4ex}
  \scalebox{1.2}{  
    \begin{tikzpicture}
      \begin{axis}[
          bar width=6pt,
          scaled ticks=false,
          tick label style={/pgf/number format/fixed},
          ybar stacked,
          enlargelimits=0.15,
          legend style={at={(0.5,-0.15)},
            anchor=north,legend columns=-1},
          symbolic x coords={0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10},
          xtick=data,
          nodes near coords,
          every node near coord/.append style={font=\tiny},
          nodes near coords align={vertical},
        ]
        \addplot coordinates {(0,25) (1,10222) (2,4956) (3,5589)
          (4,1651) (5,1457) (6, 729) (7, 471) (8, 313) (9, 137) (10, 126)};
      \end{axis}
    \end{tikzpicture}
  }
  \caption{\label{fig:distribution-contents}Histogram of number of
    \CodeIn{content} options per rule (up to 10).}
%\end{wrapfigure}
\end{figure}

>>>>

\tname{} is a technique to synthesize signature-based rules for
\nids~(\eg{}, Snort~\cite{snort} and Suricata~\cite{suricata}). The
goal of \tname\ is to create rules that captures \emph{only} the
malicious messages.

\begin{figure*}[t]
\centering
\includegraphics[trim=0 350 100 0,clip,width=0.65\textwidth]{figs/nids-workflow}
\caption{\tname\ workflow.}
\label{fig:overview}
\end{figure*}

\vspace{1ex}
\noindent\textbf{Overview.}~To create rules, \tname\ leverages (1)
benign and malicious network traffic and (2) rules from public
rulesets. Figure~\ref{fig:overview} shows the workflow of \tname{} as
a pipeline of three components, which appear numbered in the figure.
The inputs of the technique appear at the bottom of the figure whereas
the output appear at the right. \tname\ takes on input malicious and
benign traffic and a set of rules from public rulesets and produces on
output a list of plausible rules to isolate the malicious traffic.

\Mar{------------------ estou aqui}

First, it produces a
potentially overspecified rule that captures the malicious traffic
provided on input. In this step, \tname\ finds options by
\emph{reverse engineering} the positive traffic. It extracts tokens
from the malicious message and uses them to define the initial
rule. We say that this rule overfits the problem as it satisfies the
success criterion of only capturing the positive traffic, however it
is unlikely that it will be able to generalize to other attacks,
\ie{}, attacks of the same kind, but with different data. The reason
is that many options added to the rule are unimportant for
discriminating the attack. In the second step, \tname{} uses negative
examples to \emph{minimize} the rule, discarding unnecessary
options. Note that any subset of the original set of options captures
the positive traffic. The minimization step uses a population-based
gradient descent-like search to generate minimal solutions.

@@

%\begin{wrapfigure}[15]{r}{0.56\textwidth}
\begin{figure}[t!]
  \centering
%  \vspace{-4ex}
  \scalebox{1.2}{  
    \begin{tikzpicture}
      \begin{axis}[
          bar width=6pt,
          scaled ticks=false,
          tick label style={/pgf/number format/fixed},
          ybar stacked,
          enlargelimits=0.15,
          legend style={at={(0.5,-0.15)},
            anchor=north,legend columns=-1},
          symbolic x coords={0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10},
          xtick=data,
          nodes near coords,
          every node near coord/.append style={font=\tiny},
          nodes near coords align={vertical},
        ]
        \addplot coordinates {(0,25) (1,10222) (2,4956) (3,5589)
          (4,1651) (5,1457) (6, 729) (7, 471) (8, 313) (9, 137) (10, 126)};
      \end{axis}
    \end{tikzpicture}
  }
  \caption{\label{fig:distribution-contents}Histogram of number of
    \CodeIn{content} options per rule (up to 10).}
%\end{wrapfigure}
\end{figure}
